### 2019-10-01 banking.tex

\paragraph{Tax Exemption} will be discussed with meeting planning staff at
ANS Headquarters. The University of Illinois is tax exempt in the state of Illinois. 
Additionally, we will work driectly with ANS Headquarters to ensure tax 
exemption. Since ANS is incorporated under the General Not for Profit 
Corporation Act of Illinois, we expect this will be straightforward. We 
additionally expect such discussions will be facilitated by the physical 
proximity of ANS Headquarters and the University of Illinois (a 2 hour drive).

\subsubsection{Financial Oversight}
Financial integrity must be maintained when providing a conference of this size. To do so, diligent oversight will be practiced for all transactions related to the conference. Expense requests will be required for all transactions. These requests must carefully outline the reason for the purchase and the total cost. If the purchase is reoccuring, automation will be required at the time of request. These requests will require the approval of both conference chairs in addition to the financial director. Only the conference chairs and the financial director will have authority, assuming the previously mentioned permission, to complete transactions on the Busey Bank account. To ensure transparency, the financial director will update a public record containing all transactions.

>>>>

\paragraph{Tax Exemption} will be discussed with meeting planning staff at
ANS Headquarters. The University of Illinois is tax exempt in the state of Illinois. 
Additionally, we will work directly with ANS Headquarters to ensure tax 
exemption. Since ANS is incorporated under the General Not for Profit 
Corporation Act of Illinois, we expect this will be straightforward. We 
additionally expect such discussions will be facilitated by the physical 
proximity of ANS Headquarters and the University of Illinois (a 2 hour drive).

\subsubsection{Financial Oversight}
Financial integrity must be maintained when providing a conference of this size. To do so, diligent oversight will be practiced for all transactions related to the conference. Expense requests will be required for all transactions. These requests must carefully outline the reason for the purchase and the total cost. If the purchase is reoccurring, automation will be required at the time of request. These requests will require the approval of both conference chairs in addition to the financial director. Only the conference chairs and the financial director will have authority, assuming the previously mentioned permission, to complete transactions on the Busey Bank account. To ensure transparency, the financial director will update a public record containing all transactions.

### 2019-10-01 management.tex

\begin{itemize}
	\item $\large\textbf{\textit{General Co-Chair}}$\\
	In addition to the responsibilities outlined above, the General Co-Chair oversees the
	Non-technical Subcommittee, the Media Coordinator, and the Financial Subcommittee. He works with the Technical Co-Chair in talking to sponsors, companies, and planning full committee meetings. 
	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
	Technical Subcommittee. Works with the General Co-Chair to plan full committee meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Diversity Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Diversity Co-Chair is responsible for making sure the conference is as inclusive, diverse, and accessible as possible. This includes: contacting minority serving institutions to encourage their students to attend the conference, ensuring socials and dinners are accessible, verifies that the final list of speakers has adequate representation, and more. We believe the example set by UIUC will make this role a staple of future conferences.

@@

		Coordinates with ANS National to negotiate room rates and room blocks for hotels. Reserves busses for the 

@@

		Responsible for planning and organizing all catered meals for the conference. that includes contacting the catering services, reserving the venues where meals are held, and making sure the venues are staffed.

@@

		The Media Coordinator is reponsible for designing the conference website, constantly updating social media presence,

@@

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-dinari.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	$\textbf{Registration Coordinator - Jasmine Dinari}$\\
Jasmine is a frehsman studying Nuclear, Plasma, and Radiological Engineering at UIUC, as well as minors in French and Physics. She is starting research with Dr. Andruczyk, who is currently at the head of the HIDRA project. Powering the world through nuclear is one of her main interests, and she later hopes to participate in nuclear fusion research. The ANS Student Conference is an  amazing opportunity to share her interests in nuclear science. She gained organizational and leadership experience through various extracurriculars in high school and currently serves as the Professional Development Chair for the UIUC student chapter of Women in Nuclear. She plans on attending the 2020 ANS Student Conference at NC State.
\end{minipage}

>>>>

\begin{itemize}
	\item $\large\textbf{\textit{General Co-Chair}}$\\
	In addition to the responsibilities outlined above, the General Co-Chair oversees the
	Non-technical Subcommittee, the Media Coordinator, and the Financial Subcommittee. He works with the Technical Co-Chair in talking to sponsors, companies, and planning full committee meetings. 
	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
	Technical Subcommittee. Works with the General Co-Chair to plan full committee meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Diversity Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Diversity 
                Co-Chair is responsible for making sure the conference is as 
                inclusive, diverse, and accessible as possible. This includes: 
                contacting minority serving institutions to encourage their 
                students to attend the conference, ensuring socials and dinners 
                are accessible, verifying that the final list of speakers has 
                adequate representation, engaging with the national Diversity and 
                Inclusion in ANS Committee, and more. We believe the example set 
                by UIUC will make this role a staple of future conferences.

@@

		Coordinates with ANS National to negotiate room rates and room blocks for hotels. Reserves buses for the 

@@

		Responsible for planning and organizing all catered meals for 
                        the conference. That includes contacting the catering services, reserving the venues where meals are held, and making sure the venues are staffed.

@@

		The Media Coordinator is responsible for designing the conference website, constantly updating social media presence,

@@

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-dinari.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	$\textbf{Registration Coordinator - Jasmine Dinari}$\\
Jasmine is a freshman studying Nuclear, Plasma, and Radiological Engineering at UIUC, as well as minors in French and Physics. She is starting research with Dr. Andruczyk, who is currently at the head of the HIDRA project. Powering the world through nuclear is one of her main interests, and she later hopes to participate in nuclear fusion research. The ANS Student Conference is an  amazing opportunity to share her interests in nuclear science. She gained organizational and leadership experience through various extracurriculars in high school and currently serves as the Professional Development Chair for the UIUC student chapter of Women in Nuclear. She plans on attending the 2020 ANS Student Conference at NC State.
\end{minipage}

### 2019-10-01 proglog.tex

\subsubsection{Rachel Slaybaugh, UC Berkeley}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-slaybaugh.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Prof. Slaybaugh's research is based in numerical methods for neutron transport with an emphasis on supercomputing. She applies these methods to reactor design, shielding, and nuclear security and nonproliferation. Slaybaugh was a key founder of the nuclear innovation bootcamp, which seeks to train students and professionals in skills essential to innovation in nuclear energy while executing team projects. Finally, Slaybaugh has served as a Program Director at ARPA-E, developing and running their first fission energy programs. Advanced Research Projects Agency-Energy (ARPA-E) invests in research for ways to generate, use, and store energy. These projects have the potential to radically improve economic prosperity in the U.S. and environmental wellbeing. Due to her endeavors in teaching and sharing nuclear innovation, we believe that Slaybaugh's goals are aligned with the goals of this conference and would make her an excellent addition to the program. Slaybaugh has much to offer the conference with her vision and leadership.
\end{minipage}

@@

\subsection{Career Fair}
The career will be held all day on Friday, from 8am to 5pm, and on Saturday from 8am to noon. It will be held in Illini Rooms A \& B, a large space capable of holding 600 people. This space will be immediately adjacent to the poster sessions on saturday to encourage students and professionals to attend both. Together, the Illini Rooms can hold up to 900 people. Recruiters can mail bulkier items prior to their arrival in Champaign. All companies that sponsor the conference will be given a table at the career fair. Location will be decided in order of sponsorship amount and when the agreement was made. Universities may freely request a table at the career fair, while space is available. There will be rooms available at the Illini Union for companies to interview potential candidates.

@@

\vspace{0.5cm}
\noindent{
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.9\textwidth]{clintonpp.jpg}
	\captionof{figure}{Clinton Powerplant on Clinton Lake}
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\textbf{Clinton Nuclear Power Plant}\\
Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987. They currently serve over one million customers and operate 94.9$\%$ of the time. The tour will be held on Thursday morning and bus transportation will be provided. Attendees will be guided by a Clinton employee. The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.
\end{minipage}}

>>>>

\subsubsection{Rachel Slaybaugh, UC Berkeley}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-slaybaugh.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Prof. Slaybaugh's research is based in numerical methods for neutron 
        transport with an emphasis on supercomputing. She applies these methods 
        to reactor design, shielding, and nuclear security and 
        nonproliferation. Slaybaugh was a key founder of the nuclear innovation 
        bootcamp, which seeks to train students and professionals in skills 
        essential to innovation in nuclear energy while executing team 
        projects. Finally, Slaybaugh has served as a Program Director at 
        ARPA-E, developing and running their first fission energy programs. 
        Advanced Research Projects Agency-Energy (ARPA-E) invests in research 
        for ways to generate, use, and store energy. These projects have the 
        potential to radically improve economic prosperity in the U.S. and 
        environmental well-being. Due to her endeavors in teaching and sharing nuclear innovation, we believe that Slaybaugh's goals are aligned with the goals of this conference and would make her an excellent addition to the program. Slaybaugh has much to offer the conference with her vision and leadership.
\end{minipage}

@@

\subsection{Career Fair}
The career will be held all day on Friday, from 8am to 5pm, and on Saturday 
from 8am to noon. It will be held in Illini Rooms A \& B, a large space capable 
of holding 600 people. This space will be immediately adjacent to the poster 
sessions on Saturday to encourage students and professionals to attend both. Together, the Illini Rooms can hold up to 900 people. Recruiters can mail bulkier items prior to their arrival in Champaign. All companies that sponsor the conference will be given a table at the career fair. Location will be decided in order of sponsorship amount and when the agreement was made. Universities may freely request a table at the career fair, while space is available. There will be rooms available at the Illini Union for companies to interview potential candidates.

@@

\vspace{0.5cm}
\noindent{
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.9\textwidth]{clintonpp.jpg}
        \captionof{figure}{Clinton Power Plant on Clinton Lake}
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\textbf{Clinton Nuclear Power Plant}\\
Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987. They currently serve over one million customers and operate 94.9$\%$ of the time. The tour will be held on Thursday morning and bus transportation will be provided. Attendees will be guided by a Clinton employee. The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.
\end{minipage}}
